Multi-product Batch Processing Time Maximization Problem

### 2023-08-09 manuscript.tex
updating paper
modifying math model

$T$ is the batch processing time. \\

We have the problem: \\

\begin{equation}
max \quad T
\end{equation}

@@

\begin{equation}
T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

where: \\

@@

It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\

\emph{Solution for the example presented before} \\

Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\

$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T' \leq 16 \textrm{ min}$ \quad for A \\

$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T' \leq 12 \textrm{ min}$ \quad for B \\

so: \\

$T' = 12 \textrm{ min}$ \\

Then:\\

$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$ \\

$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$ \\

And so we have: \\

$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 64 \textrm{ min}$ \quad for A \\

$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 65 \textrm{ min}$ \quad for B \\

$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 43 \textrm{ min}$ \quad for A and B \\

So that: \\

$T'' = 43 \textrm{ min}$ \\

So we have: \\

$T = 55 \textrm{ min}$ \\

As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution. \\

In this case we will have: \\

$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$ \\

$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$ \\

$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$ \\

Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:

\begin{equation}
O_i + I_i = E_i \quad \forall i
\end{equation}

>>>>

$T$ is the batch processing time;

We have the problem:

$UD_i - O_i$ e $O_i - UD_i$

\begin{equation}
\label{MBPTMP01}
max \quad T
\end{equation}

@@

\begin{equation}
\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0
\end{equation}

\begin{equation}
\min\{\textrm{O} - \sum_i\{ O_i\}, \max\{0, I_i - O_i\}\} = 0
\end{equation}

\begin{equation}
\label{MBPTMP10}
T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

where:

@@

Note that there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1. Thus it is possible to use a simplification of the method presented, making $T' = 0$. In this case $S_i = \textrm{UD}_i, \forall i$. The simplified version of the method is presented below:

step 1: find $T^*$, where:
\begin{equation}
T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 2: calculate $T$, where:

\begin{equation}
T = \min \{T^* , \textrm{Z}\}
\end{equation}

It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper.

\emph{Solution for the example presented before}

Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have:

$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$

$T' \leq 16 \textrm{ min}$ \quad for A

$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$

$T' \leq 12 \textrm{ min}$ \quad for B

so:

$T' = 12 \textrm{ min}$

Then:

$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$

$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$

And so we have:

$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$

$T'' \leq 64 \textrm{ min}$ \quad for A

$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$

$T'' \leq 65 \textrm{ min}$ \quad for B

$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$

$T'' \leq 43 \textrm{ min}$ \quad for A and B

$T'' = 43 \textrm{ min}$

So we have:

$T = 55 \textrm{ min}$

As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution.

In this case we will have:

$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$

$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$

$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$

Observe that $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory. However, after determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:

\begin{equation}
D_i + O_i + I_i = P_i \quad \forall i
\end{equation}
